### 2015-07-01 doc/manual/runs.tex
Tweaks for compatibility with petsc versions prior to 3.5

>>>>

If you are interested in any of the output quantities that vary on a flux surface,
such as the density or electrostatic potential, then it is important to know
how the poloidal and toroidal angles ($\theta$ and $\zeta$) in \sfincs~are defined.
The definitions of the poloidal and toroidal angles in 
\sfincs~depend on the input parameter \parlink{geometryScheme}. When a \vmec~equilibrium is imported by setting
\parlink{geometryScheme} = 5, then \sfincs~will use the same poloidal and toroidal angles
as \vmec.  The toroidal angle in this case is the normal cylindrical coordinate. Note that field lines
are not straight in these \vmec~coordinates.
For any other setting of \parlink{geometryScheme}, \sfincs~will use Boozer coordinates.
